Clustering: A pipeline to analyse time-course gene expression data

### 2019-03-01 scripts/02_differential_expression_analysis.Rmd
FIX saving the pvalues in the right format

```{r echo=FALSE, results="hide"}
outname = ".results/pvalues.txt"
write.table(pvalues, outname, sep="\t")
```

>>>>

```{r echo=FALSE, results="hide"}
# Rename stuff for saving.
outname = ".results/pvalues.txt"
colnames(pvalues) = unlist(
    lapply(colnames(pvalues), function(x){paste0(x, "-pval")}))

colnames(qvalues) = unlist(
    lapply(colnames(qvalues), function(x){paste0(x, "-qval")}))

colnames(log_fold_change_epicon) = unlist(
    lapply(colnames(log_fold_change_epicon),
    function(x){paste0(x, "-lfc_epicon")}))

colnames(log_fold_change_max) = unlist(
    lapply(colnames(log_fold_change_max),
    function(x){paste0(x, "-lfc_max")}))

de_analysis = merge(pvalues, qvalues, all=TRUE, by="row.names")
row.names(de_analysis) = row.names(pvalues)
de_analysis = subset(de_analysis, select=-c(Row.names))

de_analysis = merge(de_analysis, log_fold_change_max, all=TRUE, by="row.names")
row.names(de_analysis) = row.names(pvalues)
de_analysis = subset(de_analysis, select=-c(Row.names))

de_analysis = merge(de_analysis, log_fold_change_epicon, all=TRUE,
		    by="row.names")
row.names(de_analysis) = row.names(pvalues)
de_analysis = subset(de_analysis, select=-c(Row.names))

write.table(de_analysis, outname, sep="\t")
```

### 2019-03-01 scripts/03_clustering.Rmd
ENH small fixes and enhancements
FIX saving the pvalues in the right format

```{r echo=FALSE, results="hide"}
# Set data files and options
data("shoemaker2015")
data = shoemaker2015$data
meta = shoemaker2015$meta

@@

	# Then rank by fisher's p-value and take max the number of genes of
	# interest
	# Filter out q-values for the pvalues table
	pval_col_to_keep = colnames(pvalues)[grepl("-pval", colnames(pvalues))]
	pvalues = pvalues[, pval_col_to_keep]
	fishers_pval = moanin:::fisher_method(pvalues)
    } else {
	genes_to_keep = names(pvalues)
    }

    if(keep_all_significant){
	genes_to_keep = names(fishers_pval[fishers_pval < 0.05])
    }else{
        genes_to_keep = names(sort(fishers_pval)[1:n_genes_to_keep])
    }
    y = as.matrix(data[genes_to_keep, ])
}else{
    y = as.matrix(data)
}

>>>>

```{r echo=FALSE, results="hide"}
# Set data files and options
data("shoemaker2015")

data = shoemaker2015$data
meta = shoemaker2015$meta

data = read.table(".results/quantile_normalized.txt")

@@

	# Then rank by fisher's p-value and take max the number of genes of
	# interest
	# Filter out q-values for the pvalues table
	pval_col_to_keep = colnames(pvalues)[grepl("-pval", colnames(pvalues))]
	pvalues = pvalues[, pval_col_to_keep]
	fishers_pval = moanin:::fisher_method(pvalues)
        if(keep_all_significant){
	   genes_to_keep = names(fishers_pval[fishers_pval < 0.05])
	}else{
	    genes_to_keep = names(sort(fishers_pval)[1:n_genes_to_keep])
	}
    }else{
	genes_to_keep = names(pvalues)
    }

    y = as.matrix(data[genes_to_keep, ])
}else{
    y = as.matrix(data)
}
